


\ifnumequal{\value{rolldice}}{0}{
  % variables 
  \renewcommand{\vbone}{9}
}{
  \ifnumequal{\value{rolldice}}{1}{
    % variables 
    \renewcommand{\vbone}{8}
  }{
    \ifnumequal{\value{rolldice}}{2}{
      % variables 
      \renewcommand{\vbone}{10}
    }{
      % variables 
      \renewcommand{\vbone}{11}
    }
  }
}

\gcalcexpr[0]{\vbtwo}{((\vbone + 2) * (\vbone + 1)) / 2}
\gcalcexpr[0]{\vbthree}{\vbone - 2}
\gcalcexpr[0]{\vbfour}{3 * (\vbone - 1)}
\gcalcexpr[0]{\vbfive}{\vbfour + 3}

\question $\vbone$ oranges have to be distributed amongst 3 children. If a child gets an orange, then 
she gets a whole orange - not half or a third or a quarter


\watchout[-30pt]

\ifprintanswers
\fi 

\begin{parts}
  \part[2] In how many ways then can the $\vbone$ oranges be distributed?  

\begin{solution}[\mcq]
  	When its a question of distributing $N$ things amongst $M$ people, imagine the $N$ things lined
  	up with $M-1$ partitions between them. The first person gets whatever is on the left of the 
  	first partition, the second what is between the first and the second partition and so on. The number 
  	of distinct distributions then is the number of distinct permutations of $N+M-1$ items where $N$
  	are of one kind and $M-1$ of the other
  	\begin{align}
  		N_{\texttt{ways}} &= \dfrac{(\vbone + 3 - 1)\,!}{\vbone\,!\cdot (3-1)\,!} = \vbtwo
  	\end{align}
  \end{solution}

  \part[2] How many of these ways are grossly unfair - meaning, one or more children do not get any oranges?

\begin{solution}[\mcq]
  	If two of the children do not get anything, then the third child must get everything. As there are only
  	3 children, there can be only 3 ways in which this can happen
  	
  	However, if only one of the three is left out, then the $\vbone$ oranges are distributed amongst the other two. 
  	Moreover, each of the other two gets \textit{atleast} one orange. So, it comes down to distributing 
  	$\vbthree$ oranges amonst two children
  	
  	\begin{align}
  		N_{\texttt{unfair}} &= 3\times\dfrac{(\vbthree + 2 - 1)\,!}{\vbthree\,!\cdot(2-1)\,!} = \vbfour
  	\end{align}
  	Hence, there are $\vbfour + 3 = \vbfive$ grossly unfair ways of distributing the $\vbone$ oranges
  \end{solution}

\end{parts}
