

\question The rate at which people enter an auditorium for a rock concert is modeled by the function $R$ given by $R(t)=1380t^2-675t^3$ for $0 \leq t \leq 2$ hours; $R(t)$ is measured in people per hour. No one is in the auditorium at time $t=0$, when the doors open. The doors close and the concert begins at time $t=2$. 

\ifprintanswers
  % stuff to be shown only in the answer key - like explanatory margin figures
\fi 

\begin{parts}
  \part[2] How many people are in the auditorium when the concert begins?
\begin{solution}[\halfpage] 
    The function we have been given $R(t)$ is actually $\dfrac{\ud}{\ud t}N(t)$, where
    $N(t)$ is the number of people inside the auditorium at any given time $t$. And therefore,
    \begin{align}
      \text{N(2)} &= \int_0^2 R(t)\ud t \\
            &= \int_0^2 1380t^2-675t^3 \ud t \\
			&= \left[1380(\dfrac{t^3}{3})-675(\dfrac{t^4}{4})\right]_0^2 \\
			&= 980
    \end{align}
  \end{solution}

  \part[2] Find the time when the rate at which people enter the auditorium is maximum. Justify your answer
\begin{solution}[\halfpage]
    The rate at which people enter - $R(t)$ - itself changes with time. And it is maximum 
    or minimum - when 
    \begin{align}
        \dfrac{\ud}{\ud t}R(t) = \dfrac{\ud}{\ud t}(1380t^2-675t^3) &= 0 \\
        \Rightarrow 2760t - 2025t^2 = t\cdot(2760 - 2025t) &= 0 \\
        \text{that is, when } t = 0, 1.363 \text{ hours} 
    \end{align}
    
    Moreover,
    \begin{align}
       \dfrac{\ud^2}{\ud t^2}(2760t - 2025t^2) &= 2760 - 4050t \\
                                   &> 0 \text{ when } t= 0 \Rightarrow \text{ minima } \\
                                   &< 0 \text { when } t = 1.363 \Rightarrow \text{ maxima }
    \end{align}
    Hence, the rate at which people enter the auditorium is \textit{lowest} when $t=0$ and
    \textit{highest} when $t=1.363$ hours
   
  \end{solution}

  \part[2] The total wait time for all the people in the auditorium is found by adding the time each person waits, starting at the time the person enters the auditorium and ending when the concert begins. The function $w$ models the total wait time for all the people who enter the auditorium before time $t$. The derivative of $w$ is given by $w'(t)=(2-t)R(t)$. Find $w(2)-w(1)$, the total wait time for those who enter the auditorium after time $t=1$. 
\begin{solution}[\halfpage]
    Let us begin by expanding $w'(t)$,
    \begin{align}
      w'(t) &= (2-t)R(t) \\
                  &= (2-t)(1380t^2-675t^3) \\
                  &= 2760t^2-2730t^3+675t^4
    \end{align}
    To compute $w(2)-w(1)$, we can solve the definite integral of $w'(t)$ from $t=1$ to $t=2$. 
    \begin{align}
      w(2)-w(1) &= \int_1^2 2760t^2-2730t^3+675t^4 \ud t \\
                            &= \left[2760(\dfrac{t^3}{3})-2730(\dfrac{t^4}{4})+675(\dfrac{t^5}{5})\right]_1^2 \\
                            &= 387.5               
    \end{align}
    The total wait time for those entering the auditorium after $t=1$ hour is $387.5$ hours.    
  \end{solution}

  \part[2] On average, how long does a person wait in the auditorium for the concert to begin? Consider all people who enter the auditorium after the doors open, and use the model for total wait time from part(c).
  \ifprintanswers
     \marginnote[5cm]{Borrowing result from part(c) Step 6}
  \fi
\begin{solution}[\halfpage]
    To find the average wait time we need to calculate the total wait time and divide it by the total number of people entering the auditorium. Let total wait time for all the people entering the auditorium be $T$.
    \begin{align}
      T &= \left[2760(\dfrac{t^3}{3})-2730(\dfrac{t^4}{4})+675(\dfrac{t^5}{5})\right]_0^2 \\
      	  &= 760
    \end{align}
    To find the total number of people who entered the auditorium, we use the result from part(a). Combining these two results, the average wait time would be,
    \begin{align}
     T_{avg} &= \dfrac{760}{980} \\
                        &= 0.77551
    \end{align}
   $0.77551$ hours or $46.53$ minutes.
  \end{solution}

\end{parts}
