

\question Consider the following scenario: A \texttt{film} has a name 
and a release date. A \texttt{studio} has a numeric id, a name and an 
address. A \text{director} has a Social Security Number (SSN) and a name. 
An \texttt{actor} has an SSN and a name. A \texttt{character} in a 
\texttt{film} has a name and a role. A \texttt{film} is produced by one 
\texttt{studio}, directed by a single \texttt{director} and has an 
\texttt{actor} playing each \texttt{character} in it.

\ifprintanswers
  \marginnote {This is a diagram}

\fi

\begin{parts}
  \part Is there a weak entity type in this schema? If yes, then show
  this weak entity type and justify why.

  \begin{solution}
    By definition a weak entity type cannot be identified uniquely by
    it's attributes alone, it relies on a foreign key which in turn is
    the primary key of a related entity.\\
    In our scenario, \texttt{character} is a weak entity. It belongs to 
    a film and to be uniquely identified, it must be referenced through 
    the \texttt{film} to which it belongs.\\
    \texttt{character} - belongs - \texttt{film}
  \end{solution}

  \part Is there a partial participation constraint in the schema? If
  yes, then show the constraint and justify why.

  \begin{solution}
    Partial participation constraints are those where the entity need
    not always participate in a relationship.\\
    In our scenario, \texttt{director} can exist without her having 
    directed a \texttt{film}, a \texttt{studio} can exist without it 
    having produced a \texttt{film} and an \texttt{actor} can exist
    without having played a \texttt{character}.\\
    \texttt{director} - directed, \texttt{studio} - produced, 
    \texttt{actor} - played
  \end{solution}

  \part Is there a total participation constraint in the schema? If there
  is, show this constraint and justify why.

  \begin{solution}
    There is a total participation constraint on a \texttt{film} in that
    it must exist for it to be directed and produced. There is also a total
    participation constraint on a \texttt{character} since it must be played.\\
    \texttt{film} - directed, \texttt{film} - produced, 
    \texttt{character} - played
  \end{solution}

\end{parts}

